Manuscript Figures for Genome Biology

### 2018-07-26 manuscript_figures/manuscript_figures.Rmd
Fix syntax in dplyr::rename

tab <- tidy_df(objects=objects, colLabels=filename, 
              fill="meanRank", annotate=NULL, alpha =0.10) %>%
  rename(filename = "casestudy") %>%
  #rename(casestudy = "filename") %>%
  mutate(filename = gsub(".rds", "", filename))

>>>>

tab <- tidy_df(objects=objects, colLabels=filename, 
              fill="meanRank", annotate=NULL, alpha =0.10) %>%
  rename(casestudy = "filename") %>%
  mutate(filename = gsub(".rds", "", filename))
